Robotic Cart System

### 2020-10-01 systemLevelFunctionalRequirements.tex
Added BU logo and draft block diagram

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{epstopdf}
\epstopdfsetup{suffix = {}}
\usepackage{siunitx}
\sisetup{unitsep = \cdot}
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...

@@

@@

\title{Robotic Cart System}
\author{Kalli Allen, Darrah Beebe, and Jason Braker \\ \underline{Advisor}: Dr. Suruz Miah}

@@

@@

@@

A block diagram of the robotic cart system is shown in \autoref{fig:sysBlockDiag}
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    % Uncomment the below line once Kalli's block diagram figure is included in the figs folder
    % \includegraphics{figs/img/sysBlockDiag}
    \caption{Block Diagram of the Robotic Cart System}
    \label{fig:sysBlockDiag}
\end{figure}

>>>>

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{epstopdf}
\epstopdfsetup{suffix = {}}
\usepackage{siunitx}
\sisetup{inter-unit-product = \cdot}
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...

@@

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Command to make the lines in the title page

@@

\title{
    \begin{center}
        \href{http://www.bradley.edu}{\includegraphics[height=1in]{figs/logoBU1-Print}}
        \vskip10pt
        \HRule \\[0.4cm]
        {\Huge \bfseries Robotic Cart System \\\Large Project Statement and Functional Requirements}\\[0.4cm] % Degree
        \HRule \\[0.4cm]
    \end{center}
    }
\author{Kalli Allen, Darrah Beebe, and Jason Braker \\ \underline{Advisor}: Dr. Suruz Miah}

@@

\setlength{\marginparwidth}{2cm}

@@

% \newpage
% \tableofcontents % Table of contents
\newpage % Start lab look on a new page

@@

A block diagram of the robotic cart system is shown in \autoref{fig:sysBlockDiag}
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=6.5in]{figs/img/sysBlockDiag}
    \caption{Block Diagram of the Robotic Cart System}
    \label{fig:sysBlockDiag}
\end{figure}
